### 2014-05-14 Paper1/paper1.tex
Did this skip a commit?

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
\textbf{Needs work.}\\
We derive and examine the parameter sensitivity of a novel modeling approach for extracting movement intent from a force-disturbed planar arm trajectory. While popular modeling approaches can be algebraically inverted to yield the same result, this more general approach reveals strengths, limitations, and underlying assumptions. After populating our model with measured lengths and masses as well as impedance values from the literature, we perform sensitivity analysis to determine the accuracy of the model relative to the uncertainty naturally inherent in point-to-point reaching. We find that sensitivity to parameter inaccuracy is on the order of microns and lower than the inaccuracy of human reaching. Further, most of the sensitivity results from uncertainty with regard to the stiffness of the joints. The robustness of this model holds promise for real-time determination of error that can free learning enhancement and treatment methods like error augmentation and challenge point from needing to prescribe explicit task goals. In addition, extraction from recorded human motion enables direct inspection of and hypothesis testing on the contents of human motor intent.

>>>>

% Please keep the abstract between 250 and 300 words
\section*{Abstract}
We derive and examine the parameter sensitivity of a novel modeling approach for extracting movement intent from a force-disturbed planar arm trajectory. While popular modeling approaches can be algebraically inverted to yield the same result, this more general approach reveals strengths, limitations, and underlying assumptions. After populating our model with measured lengths and masses as well as impedance values from the literature, we perform sensitivity analysis to determine the accuracy of the model relative to the uncertainty naturally inherent in point-to-point reaching. We find that sensitivity to parameter inaccuracy is on the order of microns and lower than the inaccuracy of human reaching. Further, most of the sensitivity results from uncertainty with regard to the stiffness of the joints. The robustness of this model holds promise for real-time determination of error that can free learning enhancement and treatment methods like error augmentation and challenge point from needing to prescribe explicit task goals. In addition, extraction from recorded human motion enables direct inspection of and hypothesis testing on the contents of human motor intent.
